An Extensible Approach to Verification of Embedded Systems

### 2014-05-02 tech-project/introduction.tex
changed some bibs

From a non-verification related perspective, a variety of tools and languages have been put forth to help make developing embedded applications a simpler, less error prone endeavor. On one end of this effort are languages such as NesC\cite{Gay:2003}, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions. The other end of this effort is largely comprised of simulation tools such as TOSSIM\cite{levis:2003}, Cooja\cite{osterlind:2006}, and Avrora that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments. Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed.

>>>>

From a non-verification related perspective, a variety of tools and languages have been put forth to help make developing embedded applications a simpler, less error prone endeavor. On one end of this effort are languages such as NesC\cite{Gay:2003}, (Network embedded sensor C) which strive to minimize concurrency issues and other common sources of error by hiding libraries of pre-written drivers underneath hierarchies of software and interface level abstractions. The other end of this effort is largely comprised of simulation tools such as TOSSIM\cite{levis:2003}, Cooja\cite{osterlind:2006}, and Avrora\cite{titzer:2005} that make use of high-fidelity simulations to model networks offline in controlled, repeatable environments. Though these and other tools have indeed proven invaluable in allowing users to test and reason about event-driven code prior to deployment, they remain incapable of providing complete assurance that code will behave as expected when deployed.
